Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-27 article.tex
Add a comparison between w and w*
typo
wording

After the hard thresholded filter $h$, they were significant differences in
peak magnitudes. Since timeseries $x_i^t$  were mainly between 0 and 1,
we smoothened the difference in peak magnitudes through
\begin{align}
g(x^t_i) = (x_i^t)^c
\end{align}
yield slightly AUROC with $c=0.9 \in (0, 1)$.

After filter $c$, we applied a filter $w^*$ similar to $w$, whose goal is also
to magnify the importance of spikes that occur in case of low global activity.
Instead of equation \ref{eq:magnify-filter}, we had
\begin{align}
 w^*(x^{t}_i) &= {(x^{t}_i + 1 )^{\left (1 + \frac{1}{\sum_{j} x^{t}_j}\right )}}^{k(\sum_{j} x^{t}_j)}
\end{align}
where the function $k$ is a piecewise linear function optimized for each filter
$f_1$, $f_2$, $f_3$ and $f_4$. For more details on this aspect, we refer the
reader to the implementation \footnote{available on
\url{https://github.com/asutera/kaggle- connectomics}.}.

@@

Since partial correlation statistics is a symmetric measure and the connectome
is a directed graph, it should be rewarding to detect the edge orientation. In
this section, we will present a heuristic trying to retrieve directivity.
However, considering results in Section \ref{sec:results}, we expect that the
additionnal gain margin should be extremely limited.

>>>>

After the hard thresholded filter $h$, they were significant differences in
peak magnitudes. Since timeseries $x_i^t$  were mainly between 0 and 1,
we smoothened these differences in peak magnitudes through
\begin{align}
g(x^t_i) = (x_i^t)^c
\end{align}
yielding slightly better AUROC with $c=0.9 \in (0, 1)$.

After filter $c$, we applied a filter $w^*$ similar to $w$, whose goal is also
to magnify the importance of spikes that occur in case of low global activity.
Instead of equation \ref{eq:magnify-filter}, we had
\begin{align}
 w^*(x^{t}_i) &= {(x^{t}_i + 1 )^{\left (1 + \frac{1}{\sum_{j} x^{t}_j}\right )}}^{k(\sum_{j} x^{t}_j)}
\end{align}
where the function $k$ is a piecewise linear function optimized for each filter
$f_1$, $f_2$, $f_3$ and $f_4$. By comparison, the filter $w$ used the following
function $k(\sum_{j} x^{t}_j) = 1$. For more details on this aspect, we refer
the reader to the implementation \footnote{available on
\url{https://github.com/asutera/kaggle- connectomics}.}.

@@

Since partial correlation statistics is a symmetric measure and the connectome
is a directed graph, it should be rewarding to detect the edge orientation. In
this section, we will present a heuristic trying to retrieve directivity.
However, considering results in Section \ref{sec:results}, we expect that the
additional gain margin should be extremely limited.
